---
title: "TidyTuesday - UN Votes"
author: "Moriah Taylor"
date: "3/23/2021"
output: html_document
---

# This Week's Data

The data this week comes from Harvard's Dataverse by way of Mine Çetinkaya-Rundel, David Robinson, and Nicholas Goguen-Compagnoni.

Original Data citation:

Citation: Erik Voeten "Data and Analyses of Voting in the UN General Assembly" Routledge Handbook of International Organization, edited by Bob Reinalda (published May 27, 2013). Available at SSRN: http://ssrn.com/abstract=2111149

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE, warning=FALSE, include=TRUE}
library(tidytuesdayR)
library(tidyverse)
library(lubridate)
library(ggdark)
library(unvotes)
library(extrafont)
library(sysfonts)
library(showtext)
library(dplyr)
library(readxl)
library(countrycode)
library(tidyr)
library(forcats)
library(Cairo)
```


# Load the Data

Download this week's data on UN Voting utilizing code made available on the TidyTuesday GitHub.
```{r, message=FALSE, warning=FALSE, include=TRUE}
# Get the Data
# Code sourced from TidyTuesday GitHub
# (https://github.com/rfordatascience/tidytuesday/tree/master/data/2021/2021-03-23)

unvotes <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-03-23/unvotes.csv')
roll_calls <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-03-23/roll_calls.csv')
issues <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-03-23/issues.csv')
```

# Data Cleaning

The data cleaning can be found in the [data-raw](https://github.com/dgrtwo/unvotes/blob/master/data-raw/un-data.R) folder of the package. 

```{r, message=FALSE, warning=FALSE, include=TRUE}
vlevels <- c("yes", "abstain", "no")

load("UNVotes2021.RData")

un_votes <- completeVotes %>%
  filter(vote <= 3) %>%
  mutate(
    country = countrycode(ccode, "cown", "country.name"),
    country_code = countrycode(ccode, "cown", "iso2c"),
    # Match based on old version of data from unvotes package
    country_code = case_when(
      country == "Czechoslovakia" ~ "CS",
      country == "Yugoslavia" ~ "YU",
      country == "German Democratic Republic" ~ "DD",
      country == "Yemen People's Republic" ~ "YD",
      TRUE ~ country_code
    ),
    country = if_else(!is.na(Countryname) & Countryname == "German Federal Republic", "Federal Republic of Germany", country)
  ) %>%
  select(rcid, country, country_code, vote) %>%
  mutate(vote = as.character(vote)) %>%
  mutate(vote = fct_recode(vote, yes = "1", abstain = "2", no = "3"))

descriptions <- completeVotes %>%
  select(session, rcid, abstain, yes, no, importantvote, date, unres, amend, para, short, descr, me, nu, di, hr, co, ec) %>%
  distinct(rcid, .keep_all = TRUE)

un_roll_calls <- descriptions %>%
  select(rcid, session, importantvote:descr) %>%
  mutate(rcid = as.integer(rcid),
         date = as.Date(date)) %>%
  arrange(rcid)

un_roll_call_issues <- descriptions %>%
  select(rcid, me:ec) %>%
  gather(short_name, value, me:ec) %>%
  mutate(rcid = as.integer(rcid),
         value = as.numeric(value)) %>%
  filter(value == 1) %>%
  select(-value) %>%
  mutate(issue = fct_recode(short_name,
                            "Palestinian conflict" = "me",
                            "Nuclear weapons and nuclear material" = "nu",
                            "Colonialism" = "co",
                            "Human rights" = "hr",
                            "Economic development" = "ec",
                            "Arms control and disarmament" = "di"))
```

# Data Exploration

```{r, message=FALSE, warning=FALSE, include=TRUE}
#find out what kinds of issues are voted on
unique(un_roll_call_issues$issue)
```

```{r, message=FALSE, warning=FALSE, include=TRUE}
#add columns for year, month, and day
un_roll_calls$year = format(as.Date(un_roll_calls$date, format="%d/%m/%Y"),"%Y")
un_roll_calls$month = format(as.Date(un_roll_calls$date, format="%d/%m/%Y"),"%m")
un_roll_calls$day = format(as.Date(un_roll_calls$date, format="%d/%m/%Y"),"%d")
```

```{r, message=FALSE, warning=FALSE, include=TRUE}
#get rcids for nuclear issues from un_roll_call_issues
nuclear_subset <- subset(un_roll_call_issues, short_name=="nu")
nuclear_rcids <- unique(nuclear_subset$rcid)

#subset un_roll_calls to only nuclear issues
nuclear_roll_calls = subset(un_roll_calls, rcid %in% nuclear_rcids)

#subset nuclear_roll_calls to cold war period
cold_war = subset(nuclear_roll_calls, year>=1947 & year<=1991)
```

```{r, message=FALSE, warning=FALSE, include=TRUE}
#tidy data to prepare for plot
cold_war_nuclear_issues <- cold_war %>%
  group_by(date) %>%
  mutate(count_issues = length(unique(rcid))) %>%
  mutate(month_decimal = as.numeric(month) * 0.08) %>%
  mutate(x_axis = as.numeric(year) + month_decimal) %>%
  select(date, year, month, day, count_issues, x_axis)
data_ = cold_war_nuclear_issues
```

```{r, message=FALSE, warning=FALSE, include=TRUE}
 #create dataframe for cold war events
event = c("Korean War", "U-2 Incident", "Cuban Missile Crisis", "Strategic Arms Limitation Talks", "Soviets Invade Afghanistan", "Reunited Germany")
x_end = c(1950.48, 1960.4, 1962.8, 1969.88, 1979.96, 1989.88)
y_end = c(2.8, 2.1, 9, 2, 14, 18)
y_ = c(4.8, 9, 14, 6, 16, 21)
events = data.frame(event, x_end, y_, y_end)
```
```{r, message=FALSE, warning=FALSE, include=TRUE}
#import custom text
font_add(family = "kalam", "Kalam-Bold.ttf")
font_add(family = "montserrat-ital", "Montserrat-Italic.ttf")
showtext.auto()
loadfonts()
```

```{r, message=FALSE, warning=FALSE, include=TRUE}
#create visualization
plot <- ggplot(data=data_, aes(x=x_axis, y=count_issues, ymax=count_issues)) + 
  geom_ribbon(ymin=-1, fill='#D25c07', alpha=0.5) +
  scale_x_continuous(
    breaks = seq(1948, 1990, 3),
    labels = paste0(seq(1948, 1990, 3)),
    limits = c(1948.56, 1991.16)
  ) +
  scale_y_continuous(
    breaks = seq(0,26,2),
    labels = paste0(seq(0,26,2)),
    limits = c(1,26),
  ) +
  labs(
    title = "GOING NUCLEAR",
    subtitle = "Number of Nuclear Issues Addressed in UN sessions during the Cold War",
    caption = "Source: UN Votes data | Moriah Taylor | Twitter: moriah_taylor58 | GitHub: moriahtaylor1"
  ) + xlab("") + ylab("") +
  theme(
    axis.text.x = element_text(size = 14), 
    axis.text.y = element_text(size = 14), 
    axis.ticks = element_blank(),
    panel.background = element_rect(fill = "#dadbde"),
    plot.background = element_rect(fill = "#dadbde"),
    panel.grid.major = element_line(color = "#848690"),
    axis.line = element_line(color = "#848690"),
    plot.title = element_text(face = "bold", hjust = 0.5, size = 25), 
    plot.subtitle = element_text(hjust = 0.5, size = 18), 
    plot.caption = element_text(size = 12)) + 
      dark_theme_light(base_family="kalam") +
  #add lines for each event
  geom_segment(aes(x=events$x_end[1], xend=events$x_end[1], y=events$y_[1], yend=events$y_end[1]), size=.3) +
  geom_segment(aes(x=events$x_end[2], xend=events$x_end[2], y=events$y_[2], yend=events$y_end[2]), size=.3) +
  geom_segment(aes(x=events$x_end[3], xend=events$x_end[3], y=events$y_[3], yend=events$y_end[3]), size=.3) +
  geom_segment(aes(x=events$x_end[4], xend=events$x_end[4], y=events$y_[4], yend=events$y_end[4]), size=.3) +
  geom_segment(aes(x=events$x_end[5], xend=events$x_end[5], y=events$y_[5], yend=events$y_end[5]), size=.3) +
  geom_segment(aes(x=events$x_end[6], xend=events$x_end[6], y=events$y_[6], yend=events$y_end[6]), size=.3) +
  #add dots for each event
  geom_point(aes(x=events$x_end[1], y=events$y_[1]), shape=16, size=2) +
  geom_point(aes(x=events$x_end[2], y=events$y_[2]), shape=16, size=2) +
  geom_point(aes(x=events$x_end[3], y=events$y_[3]), shape=16, size=2) +
  geom_point(aes(x=events$x_end[4], y=events$y_[4]), shape=16, size=2) +
  geom_point(aes(x=events$x_end[5], y=events$y_[5]), shape=16, size=2) +
  geom_point(aes(x=events$x_end[6], y=events$y_[6]), shape=16, size=2) +
  #add event info
  geom_text(aes(x= events$x_end[1], y=events$y_[1]+1, 
                label=events$event[1]), family="montserrat-ital", size=2.5) + 
  geom_text(aes(x= events$x_end[2], y=events$y_[2]+1, 
                label=events$event[2]), family="montserrat-ital", size=2.5) + 
  geom_text(aes(x= events$x_end[3], y=events$y_[3]+1, 
                label=events$event[3]), family="montserrat-ital", size=2.5) + 
  geom_text(aes(x= events$x_end[4], y=events$y_[4]+1, 
                label=events$event[4]), family="montserrat-ital", size=2.5) + 
  geom_text(aes(x= events$x_end[5], y=events$y_[5]+1, 
                label=events$event[5]), family="montserrat-ital", size=2.5) + 
  geom_text(aes(x= events$x_end[6], y=events$y_[6]+1, 
                label=events$event[6]), family="montserrat-ital", size=2.5)
plot
ggsave("nuclear_issues_plot.pdf")
```



```{r, message=FALSE, warning=FALSE, include=TRUE}
Sys.setenv(R_GSCMD = "C:/Program Files/gs/gs9.53.3/bin/gswin64c.exe")
embed_fonts("nuclear_issues_plot.pdf")
```

----------------------------------

#### TidyTuesday

Join the R4DS Online Learning Community in the weekly #TidyTuesday event!
Every week we post a raw dataset, a chart or article related to that dataset, and ask you to explore the data.
While the dataset will be “tamed”, it will not always be tidy! As such you might need to apply various R for Data Science techniques to wrangle the data into a true tidy format.
The goal of TidyTuesday is to apply your R skills, get feedback, explore other’s work, and connect with the greater #RStats community!
As such we encourage everyone of all skills to participate!